\documentclass[english]{article}
\hyphenpenalty=10000
% ------------------- Title -------------------
\newcommand{\fullname}{Steven Schaefer}
\newcommand{\email}{stschaef@iu.edu}
\date{}
\title{Tier 1 Analysis}
\author{Put into \LaTeX\ by \\ \fullname \\ \textit{\email}}


% ------------------- Packages -------------------
% Overall formatting, use these pretty much always
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgschola}
\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage{pdfpages}

% Tikz stuff. Uncomment when using

% \usepackage{tikz-cd}
% \usepackage{tikz}
% \usepackage{pgfplots}
% \pgfplotsset{compat=1.9}
% \usepgfplotslibrary{fillbetween}

% Math stuff, I'm not entirely sure what all of these do
\usepackage{multicol}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{varioref}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage{enumitem} % for autoenumeration of parts
\usepackage{mathtools} % for 'bsmallmatrix' environment

% ------------------- Math Operators -------------------
% mathbb
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}

\DeclareMathOperator{\Mat}{\text{Mat}}
\DeclareMathOperator{\GCD}{\text{GCD}}
\DeclareMathOperator{\LCM}{\text{LCM}}
\DeclareMathOperator{\Id}{\text{Id}}
\DeclareMathOperator{\id}{\text{id}}
\DeclareMathOperator{\Sym}{\text{Sym}}
\DeclareMathOperator{\Gal}{\text{Gal}}
\DeclareMathOperator{\Aut}{\text{Aut}}
\DeclareMathOperator{\Alt}{\text{Alt}}
\DeclareMathOperator{\Hom}{\text{Hom}}
\DeclareMathOperator{\Tr}{\text{Tr}}
\DeclareMathOperator{\sgn}{\text{sgn}}
\DeclareMathOperator{\rk}{\text{rk}}
\DeclareMathOperator{\Cl}{\text{Cl}}
\DeclareMathOperator{\Log}{\text{Log}}
\DeclareMathOperator{\<}{\langle}
\renewcommand{\>}{\rangle}

\renewcommand{\Im}{\text{Im}\ }
\renewcommand{\Re}{\text{Re}\ }

\newcommand{\inv}[1]{#1^{-1}}
\newcommand{\tup}[3]{#1_{#2}, \dots, #1_{#3}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\twoheadrightarrow}
\newcommand{\Legendre}[2]{\left( \dfrac{#1}{#2} \right)}

% ------------------- Theorems and Evironments -------------------
% For restarting counter after each section
% \newtheorem{theorem}{Theorem}[section] % the main one 
\newtheorem{theorem}{Theorem} % the main one
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newtheorem{problem}[theorem]{Problem}

% \newcounter{problem}
% \newenvironment{problem}[2][Problem \theproblem]
% {\refstepcounter{problem} \hiddenproblem}


\newcounter{subproblem}[theorem]
\renewcommand{\thesubproblem}{(\alph{subproblem})}
\newenvironment{subproblem}[1]{\refstepcounter{subproblem} \begin{trivlist}\item[\hspace{2em} \hskip \labelsep {\bfseries \thesubproblem} \hskip \labelsep {\bfseries #1}]}{\end{trivlist}} 


\crefname{problem}{Problem}{Problems}
\Crefname{problem}{Problem}{Problems}
\crefname{subproblem}{Problem \thetheorem}{}
\Crefname{subproblem}{Problem \thetheorem}{}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

% ------------------- Header -------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Tier 1 Analysis}
% \rhead{\textit{stschaef}}

% \renewcommand{\labelenumi}{(\roman{enumi})}


% ------------------- Document -------------------
\begin{document}
\begin{minipage}{\textwidth}
    \maketitle
    \begin{abstract}
        I was passed on an extensive collection of handwritten notes -- totaling nearly 600 pages -- for the Tier 1 Analysis Exam at Indiana University. Here I am translating it into \LaTeX, adding my own solutions, and adding any material that I view neceessary. 
        
        I currently do not know who the original author is.
    \end{abstract}
\end{minipage}

\pagebreak

\tableofcontents

\pagebreak

\section{Problems}

\begin{theorem}[Finite Intersection Property \footnote{See \cite{rudin} p.38}]
    \label{thm:finite_intersection}
    If $\{K_{\alpha}\}$ is a collection of compact subsets of a metric space $X$ such that the intersection of every finite subcollection of $\{K_{\alpha}\}$ is nonempty, then $\bigcap K_{\alpha}$ is nonempty. 
\end{theorem}

Note that this may be any collection of compact sets. No countability is assumed.

\begin{proof}[Proof of \cref{thm:finite_intersection}]
    Suppose that $\bigcap K_{\alpha}$ is empty. Fix an arbitary set $K \in \{K_{\alpha}\}$. Because $\bigcap K_{\alpha}$ is empty, for all $x \in K$ we have that $x \in K_{\alpha}^c$ for some $\alpha$. Thus, $\bigcup \left( K_{\alpha}^c \right)$ is an oper cover of $K$. 

    Because $K$ is compact there is a finite subcover, $K_{\alpha_1}^c, \dots, K_{\alpha_n}^c$. That is, $K \subset \bigcup_{i = 1}^n \left( K_{\alpha_i}^c \right)$, so 
    
    \[
        K \cap \left( \bigcap_{i = 1}^n K_{\alpha} \right) = \emptyset
    \]

    This contradicts the hypothesis that the intersection of every finite subcollection of $\{K_{\alpha}\}$ is nonempty. So we conclude that $\bigcap K_{\alpha}$ is nonempty.
\end{proof}

\begin{problem}
    A map $f:\R^m \to \R^n$ is \textit{proper} if it is continuous and $\inv{f}(B)$ is compact for each compact subset $B \subset \R^n$; $f$ is \textit{closed} if it is continuous and $f(A)$ is closed for each closed subset $A \subset \R^m$. 
    
    \begin{subproblem}{}
        \label{prob:proper_is_closed}
        Prove that any proper map $f: \R^m \to \R^n$ is closed.
    \end{subproblem}
    
    
    \begin{subproblem}{}
        \label{prob:one_to_one_closed_is_proper}
        Prove that every one-to-one closed map $f:\R^m \to \R^n$ is proper. 
    \end{subproblem}

    Supposedly this question is from August 1997, but I could find no record of this when combing through previous exams. Note that Tier 1 August 2010, \#2 touches on the same topic of proper maps. 
    
    \begin{proof}[Proof of \cref{prob:proper_is_closed}]
        Let $A \subset \R^m$ be closed. To show that $f(A)$ is closed, it is sufficient to show that $f(A)^c$ is open. 

            Let $q \in f(A)^c$ and consider $\overline{B}_{\epsilon}(q)$ the closed ball of radius $\epsilon$ about $q$. $\overline{B}_{\epsilon}(q)$ is closed and bounded in $\R^n$, so it is compact. Because $f$ is proper, we have that $\inv{f}\left( \overline{B}_{\epsilon}(q) \right)$ is also compact. Define the following sequence of decreasing compact sets,
            
            \[
                U_j = A \cap \inv{f}\left( \overline{B}_{\epsilon_j}(q) \right),
            \]
            where $\epsilon_0 = \epsilon$ and $\epsilon_{j + 1} < \epsilon_j$. Note that each $U_j$ is indeed compact, because $\inv{f}\left( \overline{B}_{\epsilon_j}(q) \right)$ is compact for all $j$ and $A$ is closed. 

            \begin{align*}
                \bigcap U_j
                & = A \cap \bigcap \inv{f}\left( \overline{B}_{\epsilon_j}(q) \right) \\
                & = A \cap \inv{f}\left( q \right) \\
                & = \emptyset
            \end{align*}
            
            The above intersection is empty by construction, as $q \in f(A)^c$.
            
            By \cref{thm:finite_intersection} -- the finite intersection property for compact sets -- because the intersection over all $U_j$'s is empty, there must be some finite subcollection of $\{U_j\}$ with empty intersection. Write this finite subcollection as $U_1, \dots, U_n$. Let $N$  be the smallest such $n$ and note because the $U_j$'s are nested, $\bigcap^N_{j=1} U_j = U_N$. 

            \begin{align*}
                \bigcap^N U_j
                & = U_N \\
                & = A \cap \inv{f}\left( \overline{B}_{\epsilon_N}(q) \right) \\
                & = \emptyset
            \end{align*}

            Thus $f(A) \cap B_{r}(q) = \emptyset$, where $r < \epsilon_N$. So $f(A)^c$ is open and we are done. 
    \end{proof}
    
    \begin{proof}[Proof of \cref{prob:one_to_one_closed_is_proper}]
        Let $B \subset \R^n$ be compact. Because $\R^n$ is Hausdorff and $B$ is compact, $B$ is also closed. By the continuity of $f$, $\inv{f}(B)$ is also closed. To further show that $\inv{f}(B)$ is closed -- and thus $f$ is proper -- we must now show that $\inv{f}(B)$ is bounded. 

        Let $K_j = \{x \in \R^m : ||x|| \geq j\}$. $K_j$ is closed in $\R^m$ for all $j$. Because $f$ is a closed map, $f(K_j)$ is likewise closed for all $j$. Thus $f(K_j) \cap B$ is compact, and $\{f(K_j) \cap B\}_{n = 1}^{\infty}$ is a decreasing sequence of compact sets. Additionally, 

        \begin{align*}
            \bigcap \left( f(K_j) \cap B \right)  
            & = B \cap \bigcap f(K_j) \\
            & = B \cap f\left( \bigcap K_j \right)
        \end{align*}

        We achieve the final equality above by using the fact that $f$ is injective, so $\bigcap f(K_j) = f\left( \bigcap K_j \right)$. Further, $\bigcap K_j = \emptyset$, so $B \cap f\left( \bigcap K_j \right) = \emptyset$. Again by \cref{thm:finite_intersection} there must be some finite collection of $\{f(K_j) \cap B\}_{n = 1}^{\infty}$ with empty intersection, and because these sets are nested there must be some index $N$ such that 

        \[
          f(K_N) \cap B = \emptyset  
        \]

        Using injectivity once again and looking at the preimages we then see,

        \[
          K_N \cap \inv{f}(B) = \emptyset  
        \]

        So for all $x \in \inv{f}(B)$, $||x|| < N$. That is, $\inv{f}(B)$ bounded and thus compact. So $f$ is then proper.
    \end{proof}
\end{problem}

\begin{problem}
    \label{prob:function_of_intersections}
    Let the function $f: \R^n \to \R^n$ satisfy the following two conditions:
    
    \begin{enumerate}
        \item \label{enum:prob:function_of_intersections_1} $f(K)$ is compact whenever $K \subset \R^n$ is compact.
        \item \label{enum:prob:function_of_intersections_2} If $\{K_n\}$ is a decreasing sequence of compact subset of $\R^n$, then 
        
        \[
            f\left(\bigcap_{n = 1}^{\infty} K_n \right) = \bigcap_{n = 1}^{\infty} f(K_n)
        \]
    \end{enumerate}

    Prove that $f$ is continuous.

    \begin{proof}[Proof of \cref{prob:function_of_intersections}]
        Let $y \in \R^n$, $\epsilon > 0$, and $K_n = \overline{B}_{1/n}(y)$. $\{K_n\}$ is a sequence of decreasing compact sets. By \cref{enum:prob:function_of_intersections_1}, $f(K_n)$ is also compact for each $n$. So $\{f(K_n)\}$ is likewise a sequence of decreasing compact sets. 

        Define $A = \R^n \setminus B_{\epsilon}(f(y))$. $A$ is closed and each $f(K_n)$ is compact, so $A \cap f(K_n)$ is also compact. By \cref{enum:prob:function_of_intersections_2}, $\bigcap f(K_n) = f\left(\bigcap K_n \right)$. So,

        \begin{align*}
            \bigcap \left(A \cap f(K_n)\right)
            & = A \cap \bigcap f(K_n) \\
            & = A \cap f\left(\bigcap K_n \right) \\
            & = A \cap f(y) \\
            & = \emptyset
        \end{align*}

        Note that the final equality above holds, as $f(y) \not \in A$ by construction of $A$. Thus by \cref{thm:finite_intersection} there exists an index $N$ such that $A \cap f(K_N) = \emptyset$. Thus, $f(K_N) \subset A^c = B_{\epsilon}(f(y))$. So for $x \in B_{\delta}(y)$ we have $f(x) \in B_{\epsilon}(f(y))$ for $\delta < \frac{1}{N}$. That is, $f$ continuous at $y$, and because $y \in \R^n$ was arbitary $f$ is continuous everywhere. 
    \end{proof}
\end{problem}

\begin{theorem}[Tier 1 August 2015, \#10] \footnote{See \cite{rudin} p.150 and p.516}
    \label{thm:unif_convergence}

    Suppose $K$ is compact, and 
    \begin{enumerate}
        \item \label{enum:thm:unif_convergence_1} $\{f_n\}$ is a sequence of continuous functions on $K$,
        \item \label{enum:thm:unif_convergence_2} $\{f_n\}$ converges pointwise to a continuous function $f$ on $K$,
        \item \label{enum:thm:unif_convergence_3} $f_n(x) \geq f_{n + 1}(x)$ for all $x \in K, n \in \N$.
    \end{enumerate}

    Then $f_n \to f$ uniformly on $K$.
\end{theorem}

\begin{proof}[Proof of \cref{thm:unif_convergence}]
    Define $g_n = f_n - f$. Note we get entirely analagous conditions on $g_n$ as were given for $f$. That is, \cref{enum:thm:unif_convergence_1,enum:thm:unif_convergence_2,enum:thm:unif_convergence_3} give us,

    \begin{enumerate}
        \item \label{enum:thm:unif_convergence_g_1} $\{g_n\}$ is a sequence of continuous functions on $K$,
        \item \label{enum:thm:unif_convergence_g_2} $\{g_n\}$ converges pointwise to 0 on $K$,
        \item \label{enum:thm:unif_convergence_g_3} $g_n(x) \geq g_{n + 1}(x)$ for all $x \in K, n \in \N$.
    \end{enumerate}
    
    To prove the desired statement, it is sufficient to show that $g_n \overset{\text{unif.}}{\to} 0$. Let $\epsilon > 0$ be given and let $E_n = \inv{g_n}([\epsilon, \infty))$. Because $g_n$ is continuous, $E_n$ is closed for all $n$. Further, $E_n$ a closed subset of  $K$ and $K$ is compact, so $E_n$ compact. Note that $E_n$ is a decreasing sequence of compact sets because of \cref{enum:thm:unif_convergence_g_3}.

    Because $g_n \overset{\text{p.w.}}{\to} 0$ on $K$, we have $\bigcap E_n = \emptyset$. So by \cref{thm:finite_intersection}, there is some index $N$ such that $E_N = \inv{g_N}([\epsilon, \infty)) = \emptyset$. So for $x \in K$, we have $0 \leq g_N(x) < \epsilon$. Further, by \cref{enum:thm:unif_convergence_g_3} we have $g_n(x) \in [0, \epsilon)$ for $n \geq N$, $x \in K$. So $g_n \overset{\text{unif.}}{\to} 0$, and thus $f_n \overset{\text{unif.}}{\to} f$.
\end{proof}

\begin{problem}
    \label{prob:ball_at_origin}
    Let $F: \R^n \to \R^n$ be a differentiable map such that $F(0) = 0$. Assume that 

    \[
      \sum_{j, k = 1}^n \left| {\partial F_j \over \partial x_k} (0) \right|^2 = c < 1.
    \]

    Prove that there is a ball $B \subset \R^n$ with center 0 such that $F(B) \subset B$.
\end{problem}

\begin{proof}[Proof of \cref{prob:ball_at_origin}]
    Because $F$ is differentiable on $\R^n$, it is in particular differentiable at 0. So there exists a linear transformation $DF(0)$ \footnote{This notation may be a little verbose, but I am choosing it here to be clear that the derivative of $F$ is a map that assigns to each point $p$ in the domain of $F$ a linear transformation $DF(p)$. Another way to write this is $DF|_p$, however this notation didn't play nice with the absolute value bars in the above TeX.} -- i.e. the Jacobian matrix evaluated at 0 -- such that,

    \begin{align*}
        0
        & = \lim_{h \to 0} \frac{|F(h) - F(0) - DF(0)(h)|}{|h|} \\
        & = \lim_{h \to 0} \frac{|F(h) - DF(0)(h)|}{|h|}
    \end{align*}

    Define $E(h) = F(h) - DF(0)(h)$ where $\lim_{h \to 0} \frac{|E(h)|}{|h|}$ \footnote{Another notational note: In this particular case, the norm of both the numerator and denominator is $| \cdot |_{\R^n}$. However in generality, the numerator and denominator do not have the same norm on them. The denominator belongs to the domain of $F$ and the numerator belongs to the codomain. Even further, it may be more clear to indicate these norms with $||\cdot||_{\R^n}$, but I am not in the habit of writing this.}. We may think of this as the error term when considering the derivative as an approxiamtion of $F$ in a neighborhood of 0. Thus,

    \[
      F(h) = DF(0)(h) + E(h)
    \]

    By the triangle inequality of $|\cdot|_{\R^n}$,

    \begin{align*}
        |F(h)| 
        & \leq |DF(0)(h)| + |E(h)| \\
        & \leq \sup \{\left|DF(0)(x)\right| : |x| = 1\} |h| + |E(h)|
    \end{align*}

    Using the substitution $A = \sup \{\left|DF(0)(x)\right| : |x| = 1\}$, we then rewrite this as,

    \begin{equation}
        \label{eqn:prob:ball_at_origin}
        \frac{|F(h)|}{|h|} \leq A + \frac{|E(h)|}{|h|}
    \end{equation}
    
    Let $x \in \R^n, |x| = 1$ and consider the coordinates of $DF(0)(x)$. 

    \begin{align*}
        (DF(0)(x))_i 
        & = \sum_{k = 1}^n {\partial F_i \over \partial x_k} (0) x_k 
    \end{align*}

    So by the triangle inequality,

    \begin{align*}
        \left| (DF(0)(x))_i \right|
        & \leq \sum_{k = 1}^n \left| {\partial F_i \over \partial x_k} (0) x_k \right| \\
        & \overset{\text{C.S. \footnotemark}}{\leq} \left( \sum \left| {\partial F_i \over \partial x_k} (0) \right|^2 \right) \left( \sum |x_k|^2 \right) \\
        & = \left( \sum \left| {\partial F_i \over \partial x_k} (0) \right|^2 \right) |x| \\
        & = \left( \sum \left| {\partial F_i \over \partial x_k} (0) \right|^2 \right)
    \end{align*}
    \footnotetext{Cauchy-Schwartz Inequality}
    
    We then use this to find the norm of $DF(0)(x)$,

    \begin{align*}
        |DF(0)(x)| 
        & = \sum_i \sum_k \left| {\partial F_i \over \partial x_k} (0) \right|^2 \\
        & = c \\
        & < 1
    \end{align*}

    Thus, $A = \sup \{\left|DF(0)(x)\right| : |x| = 1\} \leq \sqrt{c} < 1$. Because $\frac{|E(h)|}{|h|} \to 0$ as $h \to 0$, there exists $\delta > 0$ such that for $|h| < \delta$ we have $\frac{|E(h)|}{|h|} < 1 - \sqrt{c}$. Taking $B$ to be the ball of radius $\delta$ about 0, we modify \cref{eqn:prob:ball_at_origin} appropriately as,

    \begin{align*}
        \frac{|F(h)|}{|h|}
        & < \sqrt{c} + 1 - \sqrt{c} \\
        & = 1
    \end{align*}

    So $|F(h)| < |h|$ for $|h| < \delta$. That is to say, $F(B) \subset B$.
\end{proof}

\begin{problem}
    \label{prob:small_ball}
    Suppose that $E \subset \R^n$ is open and that $f: E \to \R^n$ is $C^2$. Suppose also that $f''(x_0)$ is positive definite for some $x_0 \in E$. Prove that there is $r > 0$ such that $f''(x)$ is positive definite for $x \in N_r(x_0)$.
\end{problem}

\begin{proof}[Proof of \cref{prob:small_ball}]
    Proceed by contradiction. Suppose not, then for all $r > 0$ there exists $x \in B_r(x_0)$ such that $f''(x)$ is not positive definite -- that is, for each $x$ there exists $y \neq 0$ such that $\< y, y \>_{f''(x)} \leq 0$. \footnote{I'm abusing notation a little here. $\< y, y \>_{f''(x)}$ is meant to indicate that the Hessian can act as a bilinear form. We equivalently write this expression as $\< y, y \>_{f''(x)} = \<f''(x)y, y \>_{\R^n}$.}

    Create sequences following the above pattern: for each $r_n = \frac{1}{n}$ we have some $x_n \in B_{r_n}(x_0)$ such that there is some $y_n \neq 0$ where $\< y_n, y_n \>_{f''(x_n)} \leq 0$. For convenience we may normalize $y_n$ to be unit length. This in turn makes $y_n$ a bounded sequence, as all entries in the sequence have length 1, so there is a convergent subsequence $y_{n_k} \to y$ where $|y| = 1$. 

    We wish now to show that $\<y_{n_k},y_{n_k}\>_{f''(x_{n_k})} \to \< y, y\>_{f''(x_0)}$,

    \begin{align*}
        |\< y, y\>_{f''(x_0)} - \<y_{n_k},y_{n_k}\>_{f''(x_{n_k})}|
        & \leq |\< y, y\>_{f''(x_0)} - \<y,y_{n_k}\>_{f''(x_0)}| \\
        & \ \ \ + |\< y, y_{n_k}\>_{f''(x_0)} - \<y,y_{n_k}\>_{f''(x_{n_k})}| \\
        & \ \ \ + |\< y, y_{n_k}\>_{f''(x_{n_k})} - \<y_{n_k},y_{n_k}\>_{f''(x_{n_k})}| \\
        & = I_1 + I_2 + I_3, \text{ respectively}
    \end{align*}

    \begin{align*}
        I_1
        & = |\< y, y\>_{f''(x_0)} - \<y,y_{n_k}\>_{f''(x_0)}| \\
        & = |\< y, y - y_{n_k}\>_{f''(x_0)}| \\
        & = |\<f''(x_0)y, y - y_{n_k}\>_{\R^n}| \\
        & \overset{\text{C.S.}}{\leq} |f''(x_0)y||y - y_{n_k}| \\
        & \leq ||f''(x_0)|| \ |y| \ |y - y_{n_k}| \\
        & = ||f''(x_0)||\ |y - y_{n_k}|
    \end{align*}

    where $||f''(x_0)|| = \sup \{\left|f''(x_0)(a)\right| : |a| = 1\}$ is the matrix norm. Further, $||f''(x_0)||$ is fixed and $y_{n_k} \to y$ as $k \to \infty$, so $I_1 \to 0$.
    
    \begin{align*}
        I_2
        & = |\< y, y_{n_k}\>_{f''(x_0)} - \<y,y_{n_k}\>_{f''(x_{n_k})}| \\
        & = |\<f''(x_0)y, y_{n_k}\>_{\R^n} - \< f''(x_{n_k})y, y_{n_k} \>_{\R^n}| \\
        & = |\< (f''(x_0) - f''(x_{n_k})y, y_{n_k} \>_{\R^n}| \\
        & \leq ||f''(x_0) - f''(x_{n_k}|| \ |y|\ |y_{n_k}| \\
        & = ||f''(x_0) - f''(x_{n_k}||
    \end{align*}

    $I_2 \to 0$, as $x_{n_k} \to x_0$ as $k \to \infty$ and $f$ is $C^2$ -- in particular, $f''$ continuous -- so $||f''(x_0) - f''(x_{n_k}||$ may be made arbitarily small. 

    \begin{align*}
        I_3 
        & = |\< y, y_{n_k}\>_{f''(x_{n_k})} - \<y_{n_k},y_{n_k}\>_{f''(x_{n_k})}| \\
        & \leq ||f''(x_{n_k})|| \ |y - y_{n_k}| \\
        & < M |y - y_{n_k}|
    \end{align*}

    We achieve these results on $I_3$ via a similar argument to above, and noting that $||f''(x_{n_k})||$ bounded (above by $M$). Because $y_{n_k} \to y$, $I_3$ may be made arbitarily small. Combining this with the above, 

    \begin{align*}
        |\< y, y\>_{f''(x_0)} - \<y_{n_k},y_{n_k}\>_{f''(x_{n_k})}|
        & \leq I_1 + I_2 + I_3 \\
        & = \epsilon
    \end{align*}

    For arbitarily small $\epsilon$, so $\<y_{n_k},y_{n_k}\>_{f''(x_{n_k})} \to \< y, y\>_{f''(x_0)}$. However, for sake of contradiction we assumed that $\<y_{n_k},y_{n_k}\>_{f''(x_{n_k})} \leq 0$ and it is given that $\< y, y\>_{f''(x_0)} > 0$, as $y \neq 0$. Thus, the desired statement is true by contradiction.

\end{proof}

\begin{problem}
    \label{prob:nondeg}
    Let $f: \R^n \to \R$ be $C^2$. A point $x \in \R^n$ is a \textit{critical point} of $f$ if all the partial derivatives of $f$ vanish at $x$. A critical point is \textit{nondegenerate} if the $n \times n$ matrix $\left[ {\partial^2 f \over \partial x_i \partial x_j } (x) \right]$ is non-singular. 

    Let $x$ be a nondegenerate critical point of $f$. Prove that there is an open neighborhood of $x$ which contains no other critical points (i.e. the nondegenerate critical points are isolated).
    
    \begin{proof}[Proof of \cref{prob:nondeg}]
        TODO
    \end{proof}
\end{problem}


\pagebreak

\section{Exams Through August 2020}
TODO: Uncomment when finished
% \includepdf[pages=-]{analysis-complete.pdf}

\pagebreak

% ------------------- Bibliography -------------------
\begin{thebibliography}{9}
    \bibitem{rudin}
    Rudin, Walter. \textit{Principles of Mathematical Analysis.} 3d ed, McGraw-Hill, 1976.
\end{thebibliography}

\end{document}